Group A

### 2023-08-24 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
so minor

```{r E1-latency-table-min-JH, echo=FALSE, eval=FALSE}
#summarize data for table
jh.first.fix.avg.min <- jh.first.fixation.after.verb.onset.min %>%
  group_by(verb_type) %>%
  summarise(Verb.on = round.comm(mean(von_relative.t)),
            Verb.off = round.comm(mean(voff_relative.t)),
            Det.on = round.comm(mean(det_relative.t)),
            Noun.on = round.comm(mean(noun_relative.t)))

>>>>

```{r E1-latency-table-min-JH, echo=FALSE}
#summarize data for table
jh.first.fix.avg.min <- jh.first.fixation.after.verb.onset.min %>%
  group_by(verb_type) %>%
  summarise(Verb.on = round.comm(mean(von_relative.t)),
            Verb.off = round.comm(mean(voff_relative.t)),
            Det.on = round.comm(mean(det_relative.t)),
            Noun.on = round.comm(mean(noun_relative.t)))

### 2023-08-24 group-a/E1-analysis-replication.Rmd
so minor

```{r E1-latency-table-min, echo=FALSE, eval=FALSE}
#summarize data for table
first.fix.avg.min <- first.fixation.after.verb.onset.min %>%
  group_by(verb_type) %>%
  summarise(Verb.on = round.comm(mean(von_relative.t)),
            Verb.off = round.comm(mean(voff_relative.t)),
            Det.on = round.comm(mean(det_relative.t)),
            Noun.on = round.comm(mean(noun_relative.t)))

@@

apa_table(
  E1_latency_table_min,
  caption = "Onset of first post-verb-onset saccade, relative to verb onset, verb offset, determiner onset, and noun onset, in ms.",
  font_size = "small",
   col_spanners = list(`Current Exp. 1` = c(2, 4), `Altmann $ Kamide Exp. 1` = c(5, 7))
)

>>>>

```{r E1-latency-table-min, echo=FALSE}
#summarize data for table
first.fix.avg.min <- first.fixation.after.verb.onset.min %>%
  group_by(verb_type) %>%
  summarise(Verb.on = round.comm(mean(von_relative.t)),
            Verb.off = round.comm(mean(voff_relative.t)),
            Det.on = round.comm(mean(det_relative.t)),
            Noun.on = round.comm(mean(noun_relative.t)))

@@

# apa_table(
#   E1_latency_table_min,
#   caption = "Onset of first post-verb-onset saccade, relative to verb onset, verb offset, determiner onset, and noun onset, in ms.",
#   font_size = "small",
#    col_spanners = list(`Current Exp. 1` = c(2, 4), `Altmann $ Kamide Exp. 1` = c(5, 7))
# )
